\section{Yield Curve Forecasting}
    \subsection{Stationarity and cointegration research of the bond yields}
        Stationarity and absence of cointegration are the key assumption for the correctness of many models.
        We shall test the stationarity of the bond yields and the cointegration of the yield curve and the macroeconomic variables.
        \subsubsection{Stationarity}
            In order to test the stationarity of the bond yields, we shall use the \emph{Augmented Dickey-Fuller test} (ADF test).
            The null hypothesis of the test is that the time series is non-stationary.
            The ADF test is a unit root test, which means that it determines how strongly a time series is defined by a trend.
            The test is based on the assumption that the time series is a random walk with drift.
            The test is performed using the \texttt{ur.df} function from the \texttt{urca} package in R.
            The results of the test are presented in Table \ref{tab:adftestForYields} (yields) and Table \ref{tab:adftestForYieldsDifference} (first difference).



        \subsubsection{Cointegration}
            We found out that the bond yields with 3m, 6m, and 9m time to maturity are cointegrated. Therefore, we shall drop the 
            6m bond from the models where we use the yield curve as an explanatory variable. The obtained results could be explained 
            with the so-called \emph{market segmentation hypothesis}. 
            
            The market segmentation hypothesis states that the yield curve is segmented into different maturity sectors, and the 
            yields in each sector are determined by the supply and demand for bonds in that sector, since the investors could be 
            differentiated by their investment purpose (buying short-term bonds to obtain small but guaranteed revenue, or long-term 
            bonds to hedge against the drop in the interest rate). It implies that the yields with similar maturities can be 
            cointegrated.






    \subsection{Na\"ive approach for the bond yield forecasting}
        \subsubsection{VAR and auto-ARIMA}
        \subsubsection{Segmented VAR}
        \subsubsection{GARCH}

    \subsection{Nelson-Siegel parametric model}
        Let us now remind the \emph{Nelson-Siegel model} introduced in \cite{Nelson1987} for the yield curve estimation. The 
        static NS model is defined as follows:
        \begin{equation}\label{eq:NS}
            G(T) = \beta_0 + (\beta_1+\beta_2)\frac{\tau}{T}\left(1-e^{-\frac{T}{\tau}}\right)-\beta_2  e^{-\frac{T}{\tau}},
        \end{equation}
        where $T$ is the time to maturity, $G(T)$ is the yield estimator of the government bonds from the curve basis, 
        and the parameters to be estimated are
        \begin{enumerate}
            \item $\tau$ is the 'typical' time to maturity, 
            \item $\beta_0$ is the long-run of zero-bond yields, 
            \item $\beta_1$ is the mid-run of zero-bond yields, 
            \item $\beta_2$ is the short-run of zero-bond yields.
        \end{enumerate}

        The Nelson-Siegel model offers significant advantages for yield curve estimation and interest rate forecasting. 
        Its simplicity, flexibility, stability, and market insights make it a highly valuable tool.

        The model's simplicity is evident through its use of only a few parameters, making it easy to understand and 
        interpret. Its flexibility allows for capturing both short-term fluctuations and long-term trends in interest 
        rates accurately. The stability of the model is tested and validated across different markets and economic 
        conditions, instilling confidence in its reliability.
        
        Additionally, the Nelson-Siegel model provides valuable insights into market expectations by decomposing the 
        term structure of interest rates. This information is crucial for decision-making and portfolio management. 
        The model's versatility allows for customization and extensions to meet specific needs, further enhancing its 
        applicability.
        
        We shall suggest a modification of the \emph{Dynamic Nelson-Siegel model} introduced in \cite{Diebold2006}.
        First of all, we shall discuss the original DNS model. The functional dependency of the yield curve on the 
        time to maturity $T$ is given by
        \begin{equation}\label{eq:DNS}
            G(t, T) = \beta_0(t) + \beta_1(t)\frac{\tau(t)}{T}\left(1-e^{-\frac{T}{\tau(t)}}\right)-\beta_2(t)  e^{-\frac{T}{\tau(t)}},
        \end{equation}
        where $t$ is the current time, $T$ is the time to maturity at time $t$, $\beta_0(t)$, $\beta_1(t)$, 
        $\beta_2(t)$, and $\tau(t)$ are time-varying parameters. The factors are modeled as AR(1) processes:
        \begin{equation}\label{eq:DNS_AR}
            \begin{aligned}
                \beta_0(t) &= \beta_0 + \phi_{0,1}(\beta_0(t-1)-\beta_0) + \varepsilon_{0,t}, \\
                \beta_1(t) &= \beta_1 + \phi_{1,1}(\beta_1(t-1)-\beta_1) + \varepsilon_{1,t}, \\
                \beta_2(t) &= \beta_2 + \phi_{2,1}(\beta_2(t-1)-\beta_2) + \varepsilon_{2,t}.
            \end{aligned}
        \end{equation}

        Now we shall describe our modification of the DNS model. We shall assume that the factors $\beta_0(t)$,
        $\beta_1(t)$, $\beta_2(t)$, and $\tau(t)$ are modeled as follows:




        To calibrate the suggested model we followed the steps described below:
        \begin{enumerate}
            \item Using the non-linear least squares method, we estimated the parameters of the static Nelson-Siegel for each day of the sample period.
            \item Given a set of estimated factors, we estimated the parameters of the chosen model using the standard OLS method. The models we used:
                \begin{itemize}
                    \item auto-ARIMA,
                    \item VAR(1),
                    \item Random Walk as a baseline.
                \end{itemize}
        \end{enumerate}

        It is possible to use the standard OLS method to estimate the parameters of the DNS model since there is no cointegration in the calculated time series, see Table \ref{}. 

        The results of the model calibration are presented in Table \ref{tab:DNSresults}.
        \begin{table}
            \label{tab:DNSresults}
            \centering
            \input{results/NScoefresults.tex}
            \caption{Parameters of the DNS model for 3 different forecasting models.}
        \end{table}
